TBD

### 2020-11-02 outputs/paper/paper.Rmd
Update paper.Rmd

To mimic the population as closely as possible, we need a post-stratification dataset large enough to refer to. In this report, we use the ACS(reason).

@@

- 76 different ages;
- 11 education levels
- 15 races;
- 24 income levels;
- 51 states;
- 2 options for mask wearing habits.

@@

```{r}
attach(clean_survey)
mod <- brm(binary ~ age + education_grouped + race_ethnicity + hispanic + household_income_grouped + state + extra_covid_worn_mask,
           data = clean_survey,
           family = bernoulli(),
           iter = 4000
           )

@@

```{r}
usa_00001$estimate <-
  mod %>%
  predict(newdata = usa_00001)
```

```{r}
# to get the estimated proportions and associated 95% PIs by state
res_state <- mod %>%
  tidybayes::add_predicted_draws(newdata = census_data) %>%
  rename(president_predict = .prediction) %>%  
  mutate(president_predict_prop = president_predict*prop) %>% 
  group_by(state_name, .draw) %>% 
  summarise(kept_name_predict = sum(kept_name_predict_prop)) %>% 
  group_by(state_name) %>% 
  summarise(mean = mean(kept_name_predict), 
            lower = quantile(kept_name_predict, 0.025), 
            upper = quantile(kept_name_predict, 0.975))
```

```{r, eval=FALSE}
# graph by state
res_state %>% 
  arrange(-mean) %>% 
  left_join(d %>%
              group_by(state_name, kept_name) %>%
              summarise(n = n()) %>%
              group_by(state_name) %>%
              mutate(prop = n/sum(n)) %>%
              filter(kept_name==1)) %>% 
  ggplot(aes(y = mean, x = forcats::fct_inorder(state_name), color = "MRP estimate")) + 
  geom_point() +
  coord_flip() + 
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0) + 
  ylab("proportion keeping maiden name") + 
  xlab("state") + 
  geom_point(aes(state_name, prop, color = "raw data")) +
  scale_color_manual(name = "", values = c("MRP estimate" = "black", "raw data" = "red")) + 
  theme_bw() +
  ggtitle("Proportion of women keeping maiden name after marriage")

res_state %>% 
  mutate(statename = str_to_title(state_name)) %>% 
  #mutate(statename = ifelse(state_name=="district of columbia", "District of Columbia", statename)) %>% 
  ggplot(aes(fill = mean, state = statename)) + 
  geom_statebins() +
  scale_fill_viridis_c(name = "proportion keeping name") +
  theme_void()
ggsave("state_plot.png", width = 8, height = 6)
```

>>>>

To mimic the population as closely as possible, we need a post-stratification dataset large enough to refer to. In this report, we use the ACS because the census happens less frequently than the ACS which is updated annually.

@@

- 76 different ages;
- 11 education levels
- 7 races;
- 24 income levels;
- 51 states;
- 2 options for mask wearing habits.

@@

```{r}
attach(clean_survey)
mod <- brm(binary ~ (1|age_group) + (1|education_grouped) + (1|race_ethnicity) + (1|household_income_grouped),
           data = clean_survey,
           family = bernoulli(),
           iter = 4000,
           control = list(adapt_delta = 0.98)
           )

@@
